---
title: "Lead Safe Cleveland Coalition- Progress & Resources"
output: html_document
---

Here's where we can provide some brief context- the LSCC: what it is, it's overarching goals, key partners, etc. 
<br>
<br>
Then, we can introduce the rollout plan & timeline

```{r setup, echo=FALSE, message=FALSE, warning=FALSE, include=FALSE}
# knitr::opts_chunk$set(include = FALSE)
library(mapview)
library(sf)
library(knitr)
library(DT)
library(tidyverse)
library(kableExtra)
library(gridExtra)


ro_map <- st_read("D:/ArcIMS/lscc_dashboard_draft/data/zip_map.shp")


```


### Rollout zone map

```{r echo=FALSE, message=FALSE, warning=FALSE}


ro2 <- ro_map %>% as.data.frame() %>% select(-geometry) 
by_zone <- ro2 %>% 
  filter(!is.na(zone)) %>% 
  arrange(zone, zip) %>% 
  group_by(zone) %>% 
  mutate(zip_id = row_number()) %>% 
  pivot_wider(values_from = zip, names_prefix = "zip", names_from = zip_id) %>% 
  unite(`Zip codes`, zip1:zip5, sep = ", ", remove = TRUE, na.rm = TRUE) %>% 
  rename(Zone = zone)


# ro_map %>% ggplot(aes(fill = zone)) + geom_sf() + theme_minimal() + theme(axis.text = element_blank(), panel.grid = element_blank())
mapview(ro_map, zcol = "zone")
# grid::grid.newpage()
# gridExtra::grid.table(by_zone)
# knitr::kable(by_zone, format = "pipe", padding = 0)

```

<br>
<br>

### Zip codes in rollout zones

```{r echo=FALSE, message=FALSE, warning=FALSE}
datatable(by_zone)

```


<br>
<br>

Next, maybe briefly describe our role as auditors, and then provide links to the dashboards, and to the updated list of local accredited contractors.

<br>
<br>

## LSCC Progress trackers

* [Child lead exposure and testing](leadflexdashboard.html)

* [Lead safe rental market](rental_market.html)

